\section{Experiments and Prototypes}

\subsection{E贸n Bio: Arrhythmia Detection}
We implemented the E贸n Core on a simulated sensor analyzing RR-intervals. With a reservoir size of $N=20$, the model learns the subject's Respiratory Sinus Arrhythmia (RSA) within 50 heartbeats.
\textbf{Result:} The system detected $100\%$ of injected Premature Ventricular Contractions (PVCs) by flagging deviations $>20\%$ from the predicted interval, utilizing only 1.3KB of RAM.

\subsection{TinyLM: Efficient Language Modeling}
Using a modest reservoir ($N=256$) and a Trie-compressed vocabulary structure, we trained an ESN to generate coherent char-level text.
\textbf{Result:} The approach reduced memory usage by $>50\%$ compared to standard dictionary lookups while maintaining training stability on the Mackey-Glass benchmark (MSE $0.009$).

\subsection{E贸n Voice: Keyword Spotting}
We processed audio into 4 semantic frequency bands at 50Hz. An ESN ($N=100$) was trained to detect the temporal signature of the keyword "E贸n".
\textbf{Result:} High-confidence detection ($>0.8$ probability) was achieved with a negligible false positive rate in synthetic noise tests.

\subsection{1-Bit Protocol: Energy Efficiency on ESP32 + LoRa}
We measured the energy consumption of the 1-Bit Protocol compared to standard JSON transmission on ESP32 with LoRa SX1276 at SF10, 125kHz bandwidth.

\begin{table}[h]
\centering
\caption{Energy Comparison: 1-Bit Protocol vs JSON}
\label{tab:energy}
\begin{tabular}{lccc}
\toprule
\textbf{Metric} & \textbf{1-Bit} & \textbf{JSON} & \textbf{Improvement} \\
\midrule
Packet Size (bytes) & 21 & 175 & 8.3$\times$ \\
Time on Air (ms) & 51 & 132 & 2.6$\times$ \\
Energy per TX (mJ) & 4.3 & 11.2 & 2.6$\times$ \\
TX Count (1000mAh) & 1.02M & 0.39M & 2.6$\times$ \\
\bottomrule
\end{tabular}
\end{table}

\textbf{Result:} The 1-Bit Protocol enables 2.6$\times$ more transmissions per battery charge, extending IoT sensor lifetime from approximately 4.5 days to 11.8 days on a 1000mAh LiPo battery with 30-second transmission intervals. Range tests demonstrated reliable communication up to 3km in rural environments with RSSI $>$-120 dBm.

